---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

## 1. Descriptive Statistics

### Concept: Measures of central tendency (mean, median, mode) and dispersion (variance, standard deviation, IQR).

#### R Example: Compute summary statistics for a dataset.

```{r}
data <- rnorm(100, mean = 50, sd = 10)
summary(data)
sd(data)
var(data)

```

## 2. Probability Distributions

### Concept: Normal, Binomial, Poisson, Exponential distributions.

#### R Example: Visualizing the normal distribution.

```{r}
x <- seq(-4, 4, length=100)
y <- dnorm(x, mean=0, sd=1)
plot(x, y, type="l", col="blue", main="Normal Distribution")

```

## 3. Hypothesis Testing

### Concept: t-test, ANOVA, Chi-square test, Wilcoxon signed-rank test.

#### R Example: One-sample t-test.

```{r}
set.seed(123)
sample_data <- rnorm(30, mean = 5, sd = 2)
t.test(sample_data, mu = 5)

t.test(sample_data, mu = 4)

```

## 4. Confidence Intervals

### Concept: Estimating population parameters with confidence levels.

#### R Example: Confidence interval for the mean.

```{r}
x <- rnorm(50, mean = 100, sd = 15)
t.test(x)$conf.int

```

## 5. Regression Analysis

### Concept: Simple and multiple linear regression.

#### R Example: Simple linear regression.

```{r}
x <- rnorm(100, mean = 10, sd = 5)
y <- 2*x + rnorm(100, sd = 3)
model <- lm(y ~ x)
summary(model)
```

## 6. Classification Methods

### Concept: Logistic regression, decision trees.

#### R Example: Logistic regression using glm.

```{r}
data(iris)
iris$Species <- as.numeric(iris$Species == "setosa") # Binary classification
model <- glm(Species ~ Sepal.Length + Sepal.Width, data = iris, family = binomial)
summary(model)
```


## 7. Clustering Techniques

### Concept: k-Means, hierarchical clustering.

#### R Example: k-Means clustering.

```{r}
set.seed(123)
iris_kmeans <- kmeans(iris[,1:4], centers=3)
iris_kmeans$cluster
```

## 8. Feature Selection

### Concept: LASSO regression, stepwise selection.

#### R Example: LASSO regression using glmnet.

```{r}
library(glmnet)
x <- as.matrix(iris[, 1:4])
y <- as.numeric(iris$Species)
lasso_model <- cv.glmnet(x, y, alpha = 1)
plot(lasso_model)
```

